---
title: "IDS investigation worksheet - PULL BEFORE EDITING GUYS!!!"
author: "by The Code Crunchers: Gigi, Ben, Jamie & Adam"
date: "`r Sys.Date()`"
output: html_document
---

**Note:** You can use this file as you 'working document' where you can try out various investigation ideas and keep notes about your findings. How you use and structure this file is up to you. It is recommended that you keep notes about what you are investigating and what you find as this will make the process of creating your presentation and report easier. Please note that you _do not_ need to submit this file as part of your group project.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, message = FALSE}
library(tidyverse)
library(tidymodels)
```


```{r load-data}
laptop_data <- read_csv("data/laptop_data_cleaned.csv")
```

<h3> Data Cleaning and that </h3> 

```{r creating storage_type column - Jamie}
laptop_data <- laptop_data%>% 
  mutate(, 
storage_type = case_when(
    HDD == 0 ~ "ssd",
    SSD == 0 ~ "hdd",
    .default = "both"
  ))

```

```{r adam}
laptop_data_untidy <- read.csv("data/laptop_data.csv")
laptop_data_untidy <- laptop_data_untidy%>%
  mutate(Ram = parse_number(Ram))
laptop_data_untidy <- laptop_data_untidy%>%
  mutate(Weight = parse_number(Weight))
laptop_data_untidy <- laptop_data_untidy%>%
  mutate(Second_Price = Price)
laptop_data_filtered <- laptop_data_untidy [-1192, ]
laptop_data_filtered <- laptop_data_filtered[1:1273, ]

#check
first_diff <- which(!(laptop_data$Company == laptop_data_filtered$Company & laptop_data$TypeName == laptop_data_filtered$TypeName & laptop_data$Ram == laptop_data_filtered$Ram ))
second_diff <- all(abs(laptop_data$Weight - laptop_data_filtered$Weight) < .Machine$double.eps^0.5)

##view(select(laptop_data_filtered, Ram, Weight, Company, TypeName))
##view(select(laptop_data, Ram, Weight, Company, TypeName))
##print(first_diff)
##print(second_diff)

laptop_data_merged <- cbind(laptop_data, select(laptop_data_filtered, Second_Price, Inches, ScreenResolution, Cpu, Gpu, Memory)) 

```

```{r creating storage_capacity column - Jamie}

laptop_data_tidy <- laptop_data_merged %>%
  mutate(,
         storage_capacity = HDD + SSD
         )
```

```{r filtering out laptops with 0 storage - Jamie}

laptop_data_tidy <- laptop_data_tidy%>%
  filter(,storage_capacity != 0)
#From the work Adams done, it looks like when storage_capacity = 0 that often that these laptops do have storage but its just like flash storage and I don't know if we should just get rid or them or not but thought I'd at least say x.
```



```{r calculating price in pounds  - Jamie}

laptop_data_tidy <-laptop_data_tidy %>%
 mutate(
        log_price = log(round(exp(Price) * 0.0094 , digits =2)),
        Price = round(exp(log_price),digits = 2)
        
         )


laptop_data_final <- laptop_data_tidy
```

```{r Adding GHz as a column}
laptop_data_final <- laptop_data_final%>%
  mutate(GHz = as.numeric(str_extract(Cpu, "\\d+(\\.\\d+)?(?=GHz)")))

```

```{r write-data}

write_csv(laptop_data_final, "data/laptop_data_final.csv")
```

<h3> Data Visualisation and exploring  </h3> 

=======
```{r exploratory data analysis}
laptop_data_final %>%
  summarise(across(everything(), ~sum(is.na(.))))
#there are no NA values

laptop_data_final %>%
  select(Ram, Weight, Price, Ppi, HDD, SSD,storage_capacity,Inches,log_price,GHz) %>%
  summarise(
    across(
      .cols = everything(),  
      .fns = list(
        min = ~min(. , na.rm = TRUE),
        mean = ~mean(. , na.rm = TRUE),
        median = ~median(. , na.rm = TRUE),
        max = ~max(. , na.rm = TRUE)
      )
    )
  ) %>%
  pivot_longer(
    cols = everything(),
    names_to = c("Statistic", "Variable"),
    names_pattern = "(.*)_(.*)",
    values_to = "Value"
  ) %>%
  pivot_wider(names_from = Variable, values_from = Value)

# Calculating correlations
correlation_matrix <- laptop_data_final %>%
  select_if(is.numeric) %>%
  cor(use = "complete.obs")

correlation_matrix

#closer to 1 = greater the correlation

```
**Notes:**

- There are no NA values

- RAM and Price have a strong positive correlation, meaning that higher RAM is - associated with higher prices.

- Weight has a weak positive correlation with Price, indicating that heavier laptops may have slightly higher prices.

- TouchScreen, IPS, and PPI have positive correlations with Price, suggesting that better display features are associated with higher prices.

- SSD has a strong positive correlation with Price, indicating that larger SSD storage is linked to higher prices.

- HDD has a weak negative correlation with Price, implying that larger HDD storage may result in slightly lower prices.

```{r investigating laptop types}

#in this chunk I want to gain more insight on the characteristics of the different laptop types to indicate if the existence of certain variables increase the likelihood of what laptop type the device is

laptop_data_final %>%
  count(TypeName)

#Calculating the average values for each laptop type
avg_stats <- laptop_data_final %>%
  group_by(TypeName) %>%
  summarise(
    Avg_Ram = mean(Ram, na.rm = TRUE),
    Avg_Weight = mean(Weight, na.rm = TRUE),
    Avg_Price = mean(Price, na.rm = TRUE),
    Avg_Ppi = mean(Ppi, na.rm = TRUE),
    Avg_HDD = mean(HDD, na.rm = TRUE),
    Avg_SSD = mean(SSD, na.rm = TRUE),
    Avg_log_price = mean(log_price, na.rm = TRUE),
    Avg_Inches = mean(Inches, na.rm = TRUE),
    Avg_Storage_Capacity = mean(storage_capacity, na.rm = TRUE),
    Avg_GHz = mean(GHz, na.rm = TRUE),
  )
print(avg_stats)

avg_stats_long <- avg_stats %>%
  pivot_longer(cols = starts_with("Avg_"), names_to = "Variable", values_to = "Value")

#Creating a bunch of bar charts
ggplot(avg_stats_long, aes(x = TypeName, y = Value, fill = TypeName)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  facet_wrap(~Variable, scales = "free_y") +
  labs(
    title = "Average Specifications by Laptop Type",
    x = "Laptop Type",
    y = "Average Value",
    fill = "Variable"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


#on to box plots now
variables <- c("Ram", "Weight", "Price", "Ppi", "HDD", "SSD","Log Price","Storage Capacity","Inches","GHz")

avg_stats_long <- laptop_data_final %>%
  select(TypeName, Ram, Weight, Price, Ppi, HDD, SSD, log_price, storage_capacity, Inches,GHz) %>% 
  pivot_longer(
    cols = Ram:GHz,          
    names_to = "Variable",   
    values_to = "Value"      
  )

# visualising the box plots
ggplot(avg_stats_long, aes(x = TypeName, y = Value, fill = Variable)) +
  geom_boxplot() +
  facet_wrap(~Variable, scales = "free_y") +
  theme_minimal() +
  labs(
    title = "Specifications by Laptop Type",
    x = "Laptop Type",
    y = "Value",
    fill = "Specification"
  ) +
  theme(axis.text.x = element_text(angle = 90)) 

```
<h3>Discoveries:</h3>

**2-in-1 Convertible**

•	<u>Specifications:</u> Moderate specifications across all categories.

•	<u>HDD & SSD: </u> Limited HDD capacity, but average SSD storage.

•	<u>Weight:</u> Lightweight, making it portable.

•	<u>Price:</u> Mid-range pricing compared to other categories.

•	<u>Usage: </u> Suitable for users prioritizing portability and versatility without requiring high-end performance.

**Gaming**

•	<u>Specifications:</u> High RAM and large HDD capacity.

•	<u>Price:</u> On the higher end.

•	<u>Weight: </u> Among the heaviest laptops due to extensive components.

•	<u>Usage: </u>Ideal for gamers or users needing high processing power for tasks eg 3D modeling or video editing.

**Netbook**

•	<u>Specifications: </u> Minimal specifications, including very small SSDs, RAM, and display resolution (PPI).

•	<u>Price: </u> Budget-friendly, making it the cheapest among categories.

•	<u>Weight: </u> Very lightweight and portable.

•	<u>Usage: </u> Suitable for basic tasks such as web browsing and document editing.

**Notebook**

•	<u>Specifications:</u> Balanced features, with moderate HDD, SSD, and RAM capacity.

•	<u>Price:</u> Mid-range, providing value for general-purpose users.

•	<u>Weight:</u> Medium weight.

•	<u>Usage:</u> Designed for students and professionals seeking an all-purpose laptop.

**Ultrabook**

•	<u>Specifications: </u>Higher SSD storage, average PPI, and lightweight build.

•	<u>Price: </u>Premium-priced due to sleek design and portability.

•	<u>Weight: </u>One of the lightest laptop types.

•	<u>Usage: </u>Best for business professionals who value portability and premium build quality.

**Workstation**

•	<u>Specifications:</u> High performance, featuring maximum SSD storage and high RAM.

•	<u>Price:</u> The most expensive category due to professional-grade hardware.

•	<u>Weight:</u> Heavy, reflecting the high-end components.

•	<u>Usage:</u> Suitable for heavy workloads, such as software development, simulations, and engineering tasks.


```{r general-scatter-plot-function}

 # laptop_data_final %>%
  #ggplot(,mapping = aes(x=,y=y_axis)) +
  #geom_point() +
  #geom_smooth( method = "lm")+
# theme_minimal() +
 # labs(
   # title = title,
#  )

```


```{r Price-Histogram-J}
laptop_data_final %>%
  ggplot(mapping = aes(x=Price)) +
  geom_histogram(bins = 25)+
  theme_minimal() +
  labs(
    title = "Spread of Price",
    x = "Price",
    y = "Number of Laptops"
  )
  
#Most laptops are around 100-1000 then steadily decreases
```

```{r x v Price-Scatterplots-J}


laptop_data_final %>%
  ggplot(mapping = aes(x=Ram,y=Price, color=factor(Gpu_brand))) +
  geom_point() +
  geom_smooth(, method = "lm", )+
  theme_minimal() +
  labs(
    title = "RAM against Price",
    x = "RAM",
    y = "Price",
    color = "GPU brand"
  )

laptop_data_final %>%
  ggplot(mapping = aes(x=Weight,y=Price,)) +
  geom_point() +
  geom_smooth(, method = "lm", )+
  theme_minimal() +
  labs(
    title = "Weight against Price",
    x = "Weight",
    y = "Price",
  )

laptop_data_final %>%
  ggplot(mapping = aes(x=Ppi,y=Price,)) +
  geom_point() +
  geom_smooth(, method = "lm", )+
  theme_minimal() +
  labs(
    title = "Pixels per Inches against Price",
    x = "Pixels per Inches",
    y = "Price",
  )

laptop_data_final %>%
  ggplot(mapping = aes(x=Inches,y=Price,)) +
  geom_point() +
  geom_smooth(, method = "lm", )+
  theme_minimal() +
  labs(
    title = "Inches against Price",
    x = "Inches",
    y = "Price",
  )

laptop_data_final %>%
  ggplot(mapping = aes(x=storage_capacity,y=Price,)) +
  geom_point() +
  geom_smooth(, method = "lm", )+
  theme_minimal() +
  labs(
    title = "Storage against Price",
    x = "Inches",
    y = "Price",
  )

laptop_data_final %>%
  ggplot(mapping = aes(x=GHz,y=Price,)) +
  geom_point() +
  geom_smooth(, method = "lm", )+
  theme_minimal() +
  labs(
    title = "Processor Speed  against Price",
    x = "Processor Speed (GHz)",
    y = "Price",
  )


```

Most of these have no linear relationship with price but in terms of numerical variables, RAM or Ppi is probably the best fit
(I couldn't figure out how to get these into a single plot so I did them all individually-Jamie)

```{r Bar-Charts}

averages_TypeName <-laptop_data_final %>%
  group_by(TypeName) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
averages_TypeName %>%
  ggplot(mapping = aes(x=reorder(TypeName,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average price of each type of Laptop",
    x = "Type of Laptop",
    y = "Average Price",
  )

averages_Company <-laptop_data_final %>%
  group_by(Company) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
averages_Company %>%
  ggplot(mapping = aes(x=reorder(Company,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average price of each type of Laptop",
    x = "Laptop Provider ",
    y = "Average Price",
  )

average_TouchScreen <-laptop_data_final %>%
  group_by(TouchScreen) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
average_TouchScreen %>%
  ggplot(mapping = aes(x=reorder(TouchScreen,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average price of each type of Laptop",
    x = "Touch Screen Status",
    y = "Average Price",
  )

average_Ips <-laptop_data_final %>%
  group_by(Ips) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
average_Ips %>%
  ggplot(mapping = aes(x=reorder(Ips,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average price of each type of Laptop",
    x = "Ips Status",
    y = "Average Price",
  )

average_CPU_Brand <-laptop_data_final %>%
  group_by(Cpu_brand) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
average_CPU_Brand %>%
  ggplot(mapping = aes(x=reorder(Cpu_brand,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average price of a laptop based on CPU brand",
    x = "Cpu Brand",
    y = "Average Price",
  )

average_GPU_Brand <-laptop_data_final %>%
  group_by(Gpu_brand) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
average_GPU_Brand %>%
  ggplot(mapping = aes(x=reorder(Gpu_brand,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average of price of a laptop based on GPU brand",
    x = "Gpu Brand",
    y = "Average Price",
  )

average_Os <-laptop_data_final %>%
  group_by(Os) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
average_Os %>%
  ggplot(mapping = aes(x=reorder(Os,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average of price of a laptop based on Operating System ",
    x = "Type of Operating System",
    y = "Average Price",
  )

average_storage_type <-laptop_data_final %>%
  group_by(storage_type) %>%
  summarise(across(where(is.numeric), ~ mean(.x, na.rm = TRUE)))

        
average_storage_type %>%
  ggplot(mapping = aes(x=reorder(storage_type,Price),y=Price,)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    title = "The average of price of a laptop based on Operating System ",
    x = "Type of Storage",
    y = "Average Price",
  )
```

this looks promising for looking at models/best fits
```{r x v price by company}
laptop_data_company <- laptop_data_final%>%
  filter(Company == "Acer" | Company == "Asus" | Company == "Dell" | Company == "HP"| Company == "Lenovo")%>%
  group_by(Company)

laptop_data_final %>%
  ggplot(mapping = aes(x=storage_capacity,y=Price,color = storage_type)) +
  geom_point() +
  geom_smooth(, method = "lm", )+
  theme_minimal() +
  labs(
    title = "Storage against Price",
    x = "Inches",
    y = "Price",
  )

laptop_data_company %>%
  ggplot(mapping = aes(x=Ram,y=Price, color=Company)) +
  geom_smooth(se = FALSE, method = "lm")+
  theme_minimal() +
  labs(
    title = "RAM against Price",
    x = "RAM",
    y = "Price",
    color = "Company"
  )

laptop_data_company %>%
  ggplot(mapping = aes(x=Weight,y=Price, color=Company)) +
  geom_smooth(se = FALSE, method = "lm")+
  theme_minimal() +
  labs(
    title = "Weight against Price",
    x = "Weight",
    y = "Price",
  )

laptop_data_company %>%
  ggplot(mapping = aes(x=Ppi,y=Price, color=Company)) +
  geom_smooth(se = FALSE, method = "lm")+
  theme_minimal() +
  labs(
    title = "Pixels per Inches against Price",
    x = "Pixels per Inches",
    y = "Price",
  )



```


==================

<h3> Modelling </h3> 

```{r best-fit}
price_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(Price ~ ., data=laptop_data_final) 
tidy(price_fit)
```

```{r model-with-all-variables}

#On the lecture slides it says you really only wanna use 2 numerical predictors per model 
#I'm gonna go for Ram first as it has the highest correlation.
# Also ur meant to save the testing data for one or two models at the end 

set.seed(26)
laptop_split <- initial_split(laptop_data_final)
train_data <- training(laptop_split)
test_data  <- testing(laptop_split)

price_mod <- linear_reg() %>%
  set_engine("lm")

price_rec_1 <- recipe(Price ~ Ram, data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

  
price_wflow_1 <- workflow() %>%
  add_recipe(price_rec_1)%>%
  add_model(price_mod)

price_fit_1 <- price_wflow_1 %>% 
  fit(data = train_data)

laptop_test_pred_1 <- predict(price_fit_1,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_1, truth = Price, estimate = .pred)


#First Model is pretty terrible lol, predictions are off by  238 pounds (RMSE) and adjR^2 is 0.534 I'm gonna add SSD

price_mod_2 <- linear_reg() %>%
  set_engine("lm")

price_rec_2 <- recipe(Price ~ Ram + SSD , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

  
price_wflow_2 <- workflow() %>%
  add_recipe(price_rec_2)%>%
  add_model(price_mod)

price_fit_2 <- price_wflow_2 %>% 
  fit(data = train_data)

laptop_test_pred_2 <- predict(price_fit_2,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_2, truth = Price, estimate = .pred)

# A little bit better, predictions are off by  216 pounds (RMSE) and adjR^2 is 0.616

#I'm going to try to add TypeName as  it seems that has an effect according to barplots


price_rec_3 <- recipe(Price ~ Ram + SSD + TypeName , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

  
price_wflow_3 <- workflow() %>%
  add_recipe(price_rec_3)%>%
  add_model(price_mod)

price_fit_3 <- price_wflow_3 %>% 
  fit(data = train_data)


laptop_test_pred_3 <- predict(price_fit_3,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_3, truth = Price, estimate = .pred)

#Better, adjR^2 is now 0.696 and RMSE is down to 192

#Adding Touch Screen

price_rec_4 <- recipe(Price ~ Ram + SSD + TypeName + TouchScreen , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

  
price_wflow_4 <- workflow() %>%
  add_recipe(price_rec_4)%>%
  add_model(price_mod)

price_fit_4 <- price_wflow_4 %>% 
  fit(data = train_data)

laptop_test_pred_4 <- predict(price_fit_4,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_4, truth = Price, estimate = .pred)

#RMSE is 192 and rsq is 0.696, no effect, get rid

price_rec_5 <- recipe(Price ~ Ram + SSD + TypeName + Os , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

  
price_wflow_5 <- workflow() %>%
  add_recipe(price_rec_5)%>%
  add_model(price_mod)

price_fit_5 <- price_wflow_5 %>% 
  fit(data = train_data)

laptop_test_pred_5 <- predict(price_fit_5,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_5, truth = Price, estimate = .pred)


#Increase to 0.706 and down to 189 pounds out, keep Os

price_rec_6 <- recipe(Price ~ Ram + SSD + TypeName + Os + Ips , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

  
price_wflow_6 <- workflow() %>%
  add_recipe(price_rec_6)%>%
  add_model(price_mod)

price_fit_6 <- price_wflow_6 %>% 
  fit(data = train_data)

laptop_test_pred_6 <- predict(price_fit_6,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_6, truth = Price, estimate = .pred)

# Ips has no effect, get rid

price_rec_7 <- recipe(Price ~ Ram + SSD + TypeName + Os + Cpu_brand , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

  
price_wflow_7 <- workflow() %>%
  add_recipe(price_rec_7)%>%
  add_model(price_mod)

price_fit_7 <- price_wflow_7 %>% 
  fit(data = train_data)

laptop_test_pred_7 <- predict(price_fit_7,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_7, truth = Price, estimate = .pred)

#CPU brand brings it up to 0.718 and brings rmse to 186


price_rec_8 <- recipe(Price ~ Ram + SSD + TypeName + Os + Cpu_brand+ Gpu_brand , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

price_wflow_8 <- workflow() %>%
  add_recipe(price_rec_8)%>%
  add_model(price_mod)

price_fit_8 <- price_wflow_8 %>% 
  fit(data = train_data)

laptop_test_pred_8 <- predict(price_fit_8,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_8, truth = Price, estimate = .pred)

#RMSE at 185 and RsqAdj at 0.72

price_rec_9 <- recipe(Price ~ Ram + SSD + TypeName + Os + Cpu_brand+ Gpu_brand + storage_type , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

price_wflow_9 <- workflow() %>%
  add_recipe(price_rec_8)%>%
  add_model(price_mod)

price_fit_9 <- price_wflow_9 %>% 
  fit(data = train_data)

laptop_test_pred_9 <- predict(price_fit_9,train_data) %>%
  bind_cols(train_data %>% select(Price))


rmse(laptop_test_pred_9, truth = Price, estimate = .pred)

# adjRsq and rmse no change, get rid

price_rec_10 <- recipe(Price ~ Ram + SSD + TypeName + Os + Cpu_brand+ Gpu_brand + Company , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

price_wflow_10 <- workflow() %>%
  add_recipe(price_rec_10)%>%
  add_model(price_mod)

price_fit_10 <- price_wflow_10 %>% 
  fit(data = train_data)

laptop_test_pred_10 <- predict(price_fit_10,train_data) %>%
  bind_cols(train_data %>% select(Price))

rmse(laptop_test_pred_10, truth = Price, estimate = .pred)


#increase to 0.747 and rmse of 176

price_rec_11 <- recipe(Price ~ Ram + SSD + Os + Cpu_brand+ Gpu_brand + Company , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

price_wflow_11 <- workflow() %>%
  add_recipe(price_rec_11)%>%
  add_model(price_mod)

price_fit_11 <- price_wflow_11 %>% 
  fit(data = train_data)

laptop_test_pred_11 <- predict(price_fit_11,train_data) %>%
  bind_cols(train_data %>% select(Price))

rmse(laptop_test_pred_11, truth = Price, estimate = .pred)

glance(price_fit_1)$adj.r.squared
glance(price_fit_2)$adj.r.squared
glance(price_fit_3)$adj.r.squared
glance(price_fit_4)$adj.r.squared
glance(price_fit_5)$adj.r.squared
glance(price_fit_6)$adj.r.squared
glance(price_fit_7)$adj.r.squared
glance(price_fit_8)$adj.r.squared
glance(price_fit_9)$adj.r.squared
glance(price_fit_10)$adj.r.squared
glance(price_fit_11)$adj.r.squared
8/9


```


```{r model 10}

price_rec_10 <- recipe(Price ~ Ram + SSD + TypeName + Os + Cpu_brand+ Gpu_brand  + Company  , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

price_wflow_10 <- workflow() %>%
  add_recipe(price_rec_10)%>%
  add_model(price_mod)

price_fit_10 <- price_wflow_10 %>% 
  fit(data = train_data)

laptop_test_pred_10 <- predict(price_fit_10,test_data) %>%
  bind_cols(test_data %>% select(Price))

rmse(laptop_test_pred_10, truth = Price, estimate = .pred)
glance(price_fit_10)$adj.r.squared

price_rec_12 <- recipe(Price ~ Ram + SSD + Os + Cpu_brand+ Gpu_brand  + Company  , data = train_data)%>%
  step_dummy(all_nominal(), -all_outcomes())%>%
  step_zv(all_predictors())

price_wflow_12 <- workflow() %>%
  add_recipe(price_rec_12)%>%
  add_model(price_mod)

price_fit_12 <- price_wflow_12 %>% 
  fit(data = train_data)

laptop_test_pred_12 <- predict(price_fit_12,test_data) %>%
  bind_cols(test_data %>% select(Price))

rmse(laptop_test_pred_12, truth = Price, estimate = .pred)
glance(price_fit_12)$adj.r.squared
```

Model 10 and 8 are two best models according to RMSE and adjusted R squared values, lowkey company has loads of different possibilities so it might be difficult to interpret. 








