---
title: "An analysis of the price of a laptop based on its features and specifications"
subtitle: ""
author: "By The Code Crunchers <br> Ben, Adam, Gandom, Jamie"
institute: "University of Edinburgh"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      
---

```{r install-package, include = FALSE, eval = FALSE}
# Copy and paste the following code into your console to download and install
# the `xaringan` package that contains all of the code which allows you 
# to create presentation slides in Rmarkdown
install.packages('xaringan')
install.packages("plotly")
```


```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(plotly)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}

laptop_data <- read_csv("data/laptop_data_cleaned.csv")
laptop_data_final <- read_csv("data/laptop_data_final.csv")

```

```{r include=FALSE}

#Background image
style_xaringan(
  title_slide_background_image = ""
)

style_duo_accent(primary_color = "#035AA6", secondary_color = "#23395b")

```

class: inverse, center, middle

# Background Information


---

class: center, middle

## *“To what extent can the price of a laptop be predicted based on some of its specifications”*

---

class: inverse, middle, center

# Our initial variables
```{r initial variables, echo = FALSE}

colnames(laptop_data_final)
echo = FALSE

```
---

class: center, middle

## <h2> Glossary </h2>

.pull-left[
- Hard Disk Drive (HDD) 

- Solid State Drive (SSD)
]

.pull-right[
RAM

CPU and GPU
]

---

class: middle, center

# Removing categorical variables
<h3> only numerical variables remain </h3>
```{r numerical variables, echo = FALSE}

num_col_names <- colnames(laptop_data_final)[sapply(laptop_data_final, is.numeric)]
print(num_col_names)

```

---
class: center, middle
```{r correlation matrix plot, echo=FALSE}
correlation_matrix <- laptop_data_final %>%
  select_if(is.numeric) %>%
  cor(use = "complete.obs")


cor_tidy <- as.data.frame(as.table(correlation_matrix)) %>%
  rename(Var1 = Var1, Var2 = Var2, correlation = Freq)

cor_tidier<-cor_tidy%>%
  arrange(,correlation)

cor_tidier%>%
  filter(Var2=="log_price",Var1!="Price",Var1!="log_price")%>%
ggplot( aes(x = Var1, y = Var2, fill = correlation)) +
  geom_tile(color = "white") +
  geom_text(aes(label = round(correlation, digits = 2)))+
  scale_fill_gradient2(low = "white", mid = "lightblue", high = "#23395b", midpoint = 0) +
  labs(title = "The Correlation Matrix", x = "", y = "") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```
---

class: inverse, middle, center

# Our chosen variables
```{r chosen variables, echo = FALSE}

print("Ram")
print("SSD")

```

.footnote[
[*] This was one of many visualisations we used to narrow down the variables we chose to focus on. Due to todays time restraint we've only chosen to show this one
]

---
class: center, middle
```{r Ram vs log_price, echo=FALSE, message=FALSE}

laptop_data_final %>%
  ggplot(mapping = aes(x=Ram,y=log_price,)) +
  geom_point(color="cadetblue") +
  geom_smooth(method = "lm", color="darkblue" )+
  labs(
    title = "RAM against Log Price",
    x = "RAM (GB)",
    y = "Log Price"
  )

```



---
class: center, middle
```{r log_price vs SSD, echo=FALSE, message=FALSE}
laptop_data_final %>%
  ggplot(mapping = aes(x=SSD,y=log_price))+
  geom_point(color="cadetblue") +
  geom_smooth(method = "lm", color="darkblue" )+
  labs(
    title = "SSD against Log Price",
    x = "SSD (GB)",
    y = "Log Price",
  )
```
---
class: center, middle
```{r log_price vs SSD vs Ram, echo=FALSE, message=FALSE}
p <- plot_ly(laptop_data_final,
  x = ~Ram, y = ~SSD, z = ~log_price,
  marker = list(size = 3, color = "cadetblue", alpha = 0.5, 
                line = list(color = "darkblue", width = 2))) %>%
  add_markers() %>%
  plotly::layout(scene = list(
    xaxis = list(title = "Ram"),
    yaxis = list(title = "SSD "),
    zaxis = list(title = "Log Price"),
    camera = list(eye = list(x = 2, y = 2, z = 2))
  ))

p
```
---
class: center, middle
```{r silly faceting, echo =FALSE}

laptop_data_long <- laptop_data_final %>%
  mutate(Ips = as.character(Ips), 
         TouchScreen = as.character(TouchScreen))%>%
  pivot_longer(cols = c(Company, TypeName,TouchScreen,Ips,Cpu_brand,Gpu_brand,Os,storage_type), names_to = "x_var", values_to = "x",)

ggplot(filter(laptop_data_long, x_var %in% c("Company", "Cpu_brand", "TypeName")), aes(x = x, y = log_price, fill = x))+
  geom_bar(stat = "identity", position = "dodge")+
  facet_wrap(~x_var, scales = "free_x")+
  theme_minimal()+
  labs(x = "Categorical Variables",
       y = "Ln Price"
       )+
  theme(
    legend.position = "none",
    axis.text.x = element_text(
      angle = 45, hjust = 1))

```
---
class: center, middle
```{r silly faceting 2, echo =FALSE}

laptop_data_long <- laptop_data_final %>%
  mutate(Ips = as.character(Ips), 
         TouchScreen = as.character(TouchScreen))%>%
  pivot_longer(cols = c(Company, TypeName,TouchScreen,Ips,Cpu_brand,Gpu_brand,Os,storage_type), names_to = "x_var", values_to = "x")

ggplot(filter(laptop_data_long, !x_var %in% c("Company", "Cpu_brand", "TypeName")), aes(x = x, y = log_price, fill = x))+
  geom_bar(stat = "identity", position = "dodge")+
  facet_wrap(~x_var, scales = "free_x")+
  theme_minimal()+
  labs(x = "X Variables",
       y = "Log Price"
       )+
  theme(
    legend.position = "none",
    axis.text.x = element_text(
      angle = 0, hjust = 1))+
  scale_fill_brewer(palette = "Paired")

```
---
class: inverse, center, middle

# Choosing the right fit - why choose a *linear regression* model?

- The response variable Price is numeric and continuous, making it unsuitable for logistic regression

- Linear regression effectively captures the price trend in the data

- Preferred over non-linear model to reduce the risk of overfitting
---

class: center, middle

```{r Residuals plot 2, echo = FALSE, message=FALSE}
set.seed(26)
laptop_split <- initial_split(laptop_data_final)
train_data <- training(laptop_split)
test_data  <- testing(laptop_split)

price_log_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(log_price ~ Ram + SSD + TypeName + Os + Cpu_brand+ Gpu_brand  + Company, data=train_data)

price_log_fit_aug <- augment(price_log_fit$fit)
ggplot(price_log_fit_aug, mapping = aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.5, colour = "#23395b") +
  geom_hline(yintercept = 0, color = "black", lty = "dashed") +
  labs(title = "Residuals of our linear regression model",x = "Log Price", y = "Residuals")
```
---

class: middle

# Our final model
The first few elements of the model:
```{r model-equation, echo = FALSE}
table <- tidy(price_log_fit$fit) %>%
  slice_head(n = 6) %>%
  mutate(
	  exp_estimate = round(exp(estimate),4), # used only for the interpretation
    estimate = round(estimate, 4) # only round estimate AFTER finding exp_estimate, otherwise it's inaccurate
	) %>%
  select(term, estimate, exp_estimate)
kable(table, format = "html")
```

$$
\widehat{logPrice} = 5.59 +  (0.0271 \times Ram) + (0.0009 \times SSD) + \dots
$$
---
## Numeric Variables
For every additional GB of Ram, the estimated price increases on average by a factor of 1.03

## Categorical
Each category also has a baseline:

The base line intercept has no meaning as a laptop can be of the baseline type (2-in-1 Convertibles) but a laptop cannot have 0 RAM

All else constant, and relative to 2-in-1 Convertibles:
- the price increases on average by a factor of 1.15 for Gaming Laptops
- the price decreases on average by a factor of 0.86 for Notebooks

---

class: inverse, middle

# What we found

- The best model is linear regression
- The variables with largest effect on price are the amount of RAM and amount of SSD storage
- The categorical variable with the largest effect on price is the type of laptop
- Company has influence on the price but the highest difference is only 0.17
- The company that produes the laptop does have some influence on the price enough to be included in the model but not as highly correlated as others.
- RMSE is 0.286
- Adjusted R squared is 0.717544

---

class: middle, center

#<h1> To conclude... </h1>

---

class: inverse, center, middle

# <h1> Questions? </h1>

---

#appendix in the case of extra questions?

