---
title: "Laptop Price Prediction"
author: "by Team-Name: Jamie, Gandom, Adam, Ben"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load-lib, include = FALSE}
library(tidyverse)
library(tidymodels)

```


```{r load-data, include=FALSE}
laptop_data <- read_csv("data/laptop_data_cleaned.csv")

laptop_data <- laptop_data%>% 
  mutate(, 
storage_type = case_when(
    HDD == 0 ~ "ssd",
    SSD == 0 ~ "hdd",
    .default = "both"
  ))

laptop_data_untidy <- read.csv("data/laptop_data.csv")
laptop_data_untidy <- laptop_data_untidy%>%
  mutate(Ram = parse_number(Ram))
laptop_data_untidy <- laptop_data_untidy%>%
  mutate(Weight = parse_number(Weight))
laptop_data_untidy <- laptop_data_untidy%>%
  mutate(Second_Price = Price)
laptop_data_filtered <- laptop_data_untidy [-1192, ]
laptop_data_filtered <- laptop_data_filtered[1:1273, ]

first_diff <- which(!(laptop_data$Company == laptop_data_filtered$Company & laptop_data$TypeName == laptop_data_filtered$TypeName & laptop_data$Ram == laptop_data_filtered$Ram ))
second_diff <- all(abs(laptop_data$Weight - laptop_data_filtered$Weight) < .Machine$double.eps^0.5)

laptop_data_merged <- cbind(laptop_data, select(laptop_data_filtered, Second_Price, Inches, ScreenResolution, Cpu, Gpu, Memory)) 

laptop_data_tidy <- laptop_data_merged %>%
  mutate(,
         storage_capacity = HDD + SSD
         )

laptop_data_tidy <- laptop_data_tidy%>%
  filter(,storage_capacity != 0)

laptop_data_tidy <- laptop_data_tidy %>%
  mutate(,
    Company = case_when(
      Company == "Acer" ~ "Acer",
      Company == "Asus" ~ "Asus",
      Company == "Dell" ~ "Dell",
      Company == "HP" ~ "HP",
      Company == "Lenovo" ~ "Lenovo",
      TRUE ~ "Other"
    )    
  )

laptop_data_tidy <-laptop_data_tidy %>%
 mutate(
        log_price = log(round(exp(Price) * 0.0094 , digits =2)),
        Price = round(exp(log_price),digits = 2)
        
         )


laptop_data_final <- laptop_data_tidy

laptop_data_final<-select(laptop_data_final,-Second_Price,)

laptop_data_final <- laptop_data_final%>%
  mutate(GHz = as.numeric(str_extract(Cpu, "\\d+(\\.\\d+)?(?=GHz)")))

write_csv(laptop_data_final, "data/laptop_data_final.csv")

# load your data here and any pre-processing/cleaning that you need for your report.

```


## Research Question


“To what extent can the price of a laptop be predicted based on some of its specifications and does the price level vary based upon its company”

We can use this model as a way for people to identify what laptop type and from what company to make their purchase based on a series of specifications they want. Our initial questions to investigate included: 'To what degree does the existence of various specifications influence price' and 'to what degree will companies vary their price for the same laptop type'.



## Data

Our selected data sets contain information on 1,196 laptops with 23 variables. “Laptop_data_final” is a merged dataset of two separate collections, cleaned to limit the laptops to the following specifications which we deemed as relevant in our research:

(done on the google docs, I'll paste it in when we finalise the variables we plan on analysing- g)



## Findings







## References

Kushwaha, G. P. (2023, June 15). Laptop price prediction cleaned dataset. 2024 November 13, Kaggle. 
https://www.kaggle.com/datasets/gyanprakashkushwaha/laptop-price-prediction-cleaned-dataset 

R, J. D. (2023, November 30). Laptop price prediction dataset. 2024 November 13, Kaggle. 
https://www.kaggle.com/datasets/jacksondivakarr/laptop-price-prediction-dataset 



